Automated detection of data fabrication using statistical tools

### 2018-03-20 submission/redraft.rmd
Add paragraph(s?)

>>>>

In order to test whether a distribution of independent $p$-values might be fabricated, we previously proposed using the Fisher method [@fisher1925;@10.1186/s41073-016-0012-9]. 
The Fisher method originally was intended as a meta-analytic tool, which tests whether there is sufficient evidence for an effect (i.e., right-skewed $p$-value distribution). 
This test is computed as
$$
\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
$$
where it tests for more smaller $p$-values than larger $p$-values across the $k$ number of $p$-values. 
Reversing this results in
$$
\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
$$
where it now tests for more larger $p$-values than smaller $p$-values across the $k$ number of $p$-values that fall above the threshold $t$ (i.e., the Fisher method now tests for left-skew). 
When $t=0$, all $p$-values are selected. 
When $t>0$ the remaining $p$-values are rescaled to fit the original 0-1 range (i.e., dividing by $1-t$). 
This test is similar (but not equivalent) to Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
